---
title: "EV Titer Check"
author: "Jeremy Leipzig"
date: "12/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/leipzig/R/batch_titration_docker/')
library(cytovasTools)
library(flowFramePlus)
library(flowCore)
library(yaml)
library(magrittr)
```

## Titer Check

The titer check is designed to detect two events:
- Depletion of antibody 
- Accumulation of rocks

A reference set of individually stained 

Unstained control buffer but not antibody

Stained buffer (not plasma), now at 200mw, can be used for both depletion and rocks analysis. Any signal coming from above the background (established from `unstained`) is aggregated antibody. 

```{r configSetup}
# assume they are interested in any parameter that has an antibody
config<-yaml.load_file("config.yaml")
flowFrames<-list('ref'=list(),'sub'=list())
thresholdsObjects<-list('ref'=list(),'sub'=list())
thresholds<-list('ref'=list(),'sub'=list())
detectors<-list('ref'=list(),'sub'=list())
uuids<-list('ref'=list(),'sub'=list())
shortnames<-list('ref'=list(),'colored'=list())
```

```{r metasetup}
#[1] "AF647"      "APC_H7"     "APC_R700"   "PE"         "PE_Cy7"     "PerCP_Cy55" "V450"       "V500"       "unstained" 
shortnames[['ref']]<-names(config$reference_files)
uuids[['ref']]<-as.character(config$reference_files[names(config$reference_files)])

filelists<-list('ref'=list(),'sub'=list())
filelists[['ref']]<-config$reference_files

#names(filelists[['sub']])

#todo: handle multiple subsequent submissions
#filelists[['sub']]<-config$subsequent_files
filelists[['sub']]<-config$subsequent_files[[1]]


extractFcsMetadata<-function(fcsuuid){
  fcsdf<-data.frame(uuid=fcsuuid)
  ffp<-flowFramePlus$new(paste("cytovas-instrument-files",fcsuuid,sep="/"))
  meta<-flowCore::description(ffp$ffOrig)[c('EXPERIMENT NAME','$FIL','$DATE','EXPORT TIME','GUID')]
  names(meta)<-c("expName","fileName","date","exportTime","GUID")
  meta$parsedDate<-format(lubridate::dmy_hms(meta$exportTime),"%Y-%m-%d")
  return(cbind(fcsdf,data.frame(meta)))
}

```


## FCS Metadata
```{r fcsmeta}
rbind(plyr::ldply(filelists$ref,extractFcsMetadata),plyr::ldply(filelists$sub,extractFcsMetadata)) %>% dplyr::select(.id,uuid,expName,fileName,date) -> displaymeta
knitr::kable(displaymeta)
```


#the subsequent files are not named by anything useful, so extract their date of creation
#names(filelists[['sub']])<-paste("sub",sapply(lapply(filelists[['sub']],extractFcsMetadata),'[[','parsedDate'),sep='_')

```{r getThresholds}
#a cohort refers to the reference(ref) or subsequent(sub) files
getThresholds<-function(cohort){
  for(shortname in names(filelists[[cohort]])){
    cat(shortname,"\n")
    flowFrames[[cohort]][[shortname]]<<-flowFramePlus$new(paste("cytovas-instrument-files",filelists[[cohort]][[shortname]],sep="/"))
    
    #do I apply compensation to multistained?
    #no spillover matrix was collected
    #for ev's the spillover occurs near high SSC levels and we can ignore it
    
    isUnstained<-(shortname=='unstained')
    thresholdsObjects[[cohort]][[shortname]]<<-thresholds.from.triton(flowFrames[[cohort]][[shortname]],unstained=isUnstained)
    thresholds[[cohort]][[shortname]]<<-thresholdsObjects[[cohort]][[shortname]][['thresh']]
    detectors[[cohort]][[shortname]]<<-thresholdsObjects[[cohort]][[shortname]][['detectors']]
  }
}

getThresholds('ref')

getThresholds('sub')

#[1] "670/30 Red-A"    "780/60 Red-A"    "712/21 Red-A"    "575/25 Blue-A"   "780/60 Blue-A"   "695/40 Blue-A"   "450/50 Violet-A" "525/50 Violet-A"
wavelengths<-as.character(detectors[['ref']][names(detectors[['ref']])!="unstained"])

#[1] "AF647"      "APC_H7"     "APC_R700"   "PE"         "PE_Cy7"     "PerCP_Cy55" "V450"       "V500"   
shortnames[['colored']]<-names(detectors[['ref']][names(detectors[['ref']])!="unstained"])

```

## Conjugate table
```{r conjugate}
knitr::kable(col.names=shortnames[['colored']],rbind(wavelengths))
```

## Depletion analysis
```{r depletion}

#unstained (plasma but no antibody)
unstained_df<-data.frame(do.call(rbind,list(as.numeric(thresholds$ref$unstained[wavelengths]))))
names(unstained_df)<-shortnames$colored
row.names(unstained_df)<-"reference unstained (UA)"

singlestained_df<-data.frame(do.call(rbind,list(as.numeric(thresholds$ref[shortnames$colored]))))
names(singlestained_df)<-shortnames$colored
row.names(singlestained_df)<-"reference single-stained (SS)"

#the wavelength order is totally different
#multistained_df<-t(data.frame(thresholds$sub))[,wavelengths]
multistained_df<-data.frame(t(data.frame(thresholds$sub$fullystained)),check.names = FALSE)[,wavelengths]
row.names(multistained_df)<-"subsequent fully-stained (FS)"

#this assumes the conjugates/wavelengths are in the same order, can we guarantee this?
names(multistained_df)<-shortnames[['colored']]

sampleTable<-rbind(singlestained_df,unstained_df)

sampleTable["unboundAntibody (SS-UA)",]<-sampleTable[1,]-sampleTable[2,] #ss-ua
sampleTable<-rbind(sampleTable,multistained_df)


#stained (plasma + antibody)
knitr::kable(sampleTable, digits = 3)

#plot
ggTable<-sampleTable
ggTable$sample<-row.names(ggTable)

```

## Rocks
```{r rocks, warning=FALSE}
plot_all_conjugates_vs_ssc(flowFrames$sub$fullystained)

#anything to the right of the threshold
```

